A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-05-23 paper/theor-experiment.tex
using pyopaltools

After collection of the data for all four experiments, several metrics
were compared, including number of generations completed in twenty four hours,
Pareto fronts at $s_1$ and $s_2$, and the design variables at the Pareto front. 
From Table \ref{extable}, we clearly see ex-3 is significantly 
slower, as it evaluated about 30 to 40 fewer generations than the other experiments.
Perhaps this trade off would be acceptable if the Pareto front was significantly 
improved, but from Fig. \ref{expareto}, we can see this is not the case.
The Pareto fronts at $s_1$, are nearly identical. We could expect
they would continue to converge given more time. 
When looking at the Pareto front for $s_2$, we see ex-4 has a slight 
edge over the others.  
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{Report/ex-pareto1}%
	\llap{\raisebox{1.8cm}{%  move next graphics to top right corner
			\includegraphics[height=5.5cm]{Report/ex-pareto2}%
	}}
	\caption{My overlay figure.}
\end{figure}

\begin{figure}
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Report/ex-pareto1}
		\caption{Pareto fronts at $s_1$.}
		\label{expareto1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
	\centering
	\includegraphics[width=\textwidth]{Report/ex-pareto2}
	\caption{Pareto fronts at $s_2$.}
	\label{expareto2}
	\end{subfigure}
	\caption{Comparison of Pareto fronts for initial optimization experiments.}
	\label{expareto}
\end{figure}

Next compare the design variables at each point on the 
Pareto front.
\begin{figure}
	\centering
	\begin{subfigure}{1\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Report/ex-pareto1}
		\caption{Pareto fronts at $s_1$.}
		\label{bounds1}
	\end{subfigure}
	\begin{subfigure}{1\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Report/ex-pareto2}
		\caption{Pareto fronts at $s_2$.}
		\label{bounds2}
	\end{subfigure}
	\caption{Comparison of design variables for each Pareto front.}
	\label{bounds}
\end{figure}

The initial number of individuals was fixed at 656, 
and the minimum number individuals in later generations was fixed at 328. 
These numbers we in part based on the architecture of the KNL's. 
Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
we wanted a large population size that would fit evenly on these resources.

>>>>

After collection of the data for all four experiments, several metrics
were compared, including number of generations completed in twenty four hours,
Pareto fronts at $s_1$ and $s_2$, and the design variables at the Pareto front. 
From Table \ref{extable}, we clearly see ex-3 is significantly 
slower, as it evaluated about 30 to 40 fewer generations than the other experiments.
Perhaps this trade off would be acceptable if the Pareto front was significantly 
improved, but from Fig. \ref{expareto}, we can see this is not the case.
The Pareto fronts at $s_1$, are nearly identical. We could expect
they would continue to converge given more time. 
When looking at the Pareto front for $s_2$, we see ex-4 has a slight 
edge over the others. 
\begin{figure}[h]
	\centering
	\begin{subfigure}{0.8\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Report/ex-pareto1}
		\caption{Pareto fronts at $s_1$.}
		\label{expareto1}
	\end{subfigure}
	\begin{subfigure}{0.8\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Report/ex-pareto2}
		\caption{Pareto fronts at $s_2$.}
		\label{expareto2}
	\end{subfigure}
	\caption{Comparison of Pareto fronts for initial optimization experiments.}
	\label{expareto}
\end{figure}
\iffalse 
\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{Report/ex-pareto1}%
	\llap{\raisebox{1.8cm}{%  move next graphics to top right corner
			\includegraphics[height=5.5cm]{Report/ex-pareto2}%
	}}
	\caption{Comparison of Pareto fronts for initial optimization experiments.}
\end{figure}  
\begin{figure}
	\centering
	\begin{subfigure}{0.49\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Report/ex-pareto1}
		\caption{Pareto fronts at $s_1$.}
		%\label{expareto1}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
	\centering
	\includegraphics[width=\textwidth]{Report/ex-pareto2}
	\caption{Pareto fronts at $s_2$.}
	%\label{expareto2}
	\end{subfigure}
	\caption{Comparison of Pareto fronts for initial optimization experiments.}
	%\label{expareto}
\end{figure}
\fi

Next we compared the design variables at each point on several of the Pareto fronts. 
We eliminate ex-3 from this exercise due to it's significantly slower execution time.
There is no

Since there was no clear advantage in the design variables, we choose
the best Pareto front in Fig. \ref{expareto2}, ex-4, for an extended optimization run. 
The initial number of individuals was fixed at 656, 
and the minimum number individuals in later generations was fixed at 328. 
These numbers were in part based on the architecture of the KNL's. 
Each simulation takes 8 cores, and there are 64 cores per KNL node, 
we wanted a large population size that would fit evenly on these resources. 
We allowed the simulation to run for 200 generations.5
